\begin{center}
\LARGE\textbf {Abstract}
\end{center}
\vspace{1cm}

\begin{spacing}{1} 
\noindent
Write the abstract here.

In accordance with the Academic Regulations the thesis must contain an abstract preferably not exceeding 200 words, bound in to precede the thesis. The abstract should appear on its own, on a single page.  The format should be the sameas that of the main text. The abstract should provide a synopsis of the thesis and shall state clearly the nature and scope of the research undertaken and of the contribution made to the knowledge of the subject treated. There should be a brief statement of the method of investigation where appropriate, an outline of the major divisions or principal arguments of thework and a summary of any conclusions reached. The abstract must follow the Title Page.

Thesis guidelines can be found at: \\ \url{https://www.hw.ac.uk/uk/students/doc/guidelinesonsubmissionandformatofthesis.pdf }

\textbf{The Introduction Chapter gives some more details, and provides an introduction to the features contained in this template}

\textit{Disclaimer and Statement of Intent} - This is an unofficial LaTeX template, updated by me, Alex. I am not an expert, so there may be small issues, but I have tested this offline in TeXworks, and online in Overleaf and it works in both those cases. I just did this to be nice, the spirit of education should encourage us all to help each other, even in the small ways. If this helps you save time and some annoyance, maybe think about some way you could make another persons life a little easier? \\ As David Graeber put it: `\textit{the ultimate, hidden truth of the world is that it is something that we make, and could just as easily make differently.}'

\end{spacing}